Quality measure notes

### 2021-05-10 StateOfPractice/Ao-Report/13MeasurementMethods.tex
updated the outlines

@@

@@

>>>>

It might be a good idea to make the methods general and independent to domains.

@@

\section{Domain Selection}
How do we choose SCS domains, and point out again that the whole section should be able to apply to most domains.

@@

\section{Interviewee Selection}

Generally speaking, ask all the teams which we can find contacts, and continue with the ones who are willing to participate.

\section{Interview Question Selection}

The aspects we focused on.

\section{Interview Methods}

The way to ask questions, the way to transcript answers and the technologies used.
